When are Fuzzy Extractors Possible?

### 2014-09-22 trunk/info-bounds/FuzzyExtPossibility.tex
editing and notational fixes

 \documentclass[11pt]{article}
\def\shownotes{1}

@@

\ifnum\shownotes=1
\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
\else
\newcommand{\authnote}[2]{}
\fi
\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
\newcommand{\rnote}[1]{{\authnote{Ran}{#1}}}
\newcommand{\onote}[1]{{\authnote{Omer}{#1}}}

@@

\title{When are Fuzzy Extractors Possible?}
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this
work was sponsored by the Department of the Air Force under Air Force
Contract
\#FA8721-05-C-0002.  Opinions,
interpretations, conclusions and recommendations are those of the author
and
are not necessarily endorsed by the United States Government.  Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University and Harvard University.  Email: {\tt asmith@psu.edu}.  }}

\begin{document}
\maketitle

@@

Ideally, key derivation should be possible whenever a negligible portion of $W$ lies within a ball~(arbitrarily centered) of radius $t$.  We call the maximum weight that lies within any ball of radius $t$ the fuzzy min-entropy of a distribution.  In interactive information-reconciliation, fuzzy min-entropy is both a necessary and sufficient condition for security.

Current techniques for constructing fuzzy extractors lie far from this necessary condition.  We investigate whether this is inherent for both fuzzy extractors and secure sketches~(a one round information-reconciliation component).  Our results are centered on feasibility and our constructions and impossibility results are primarily information-theoretic.  We consider two types of fuzzy extractors and secure sketches.  The first we call \emph{distribution-aware}, the algorithms know the precise distribution they are trying to correct.  The second is \emph{distribution-oblivious} where $(\gen, \rep)$ must work for a family of distributions.

\textbf{Distribution-Aware} In the distribution-aware setting we show that whenever the fuzzy min-entropy is super-logarithmic, there exists a secure sketch and fuzzy extractor with super-logarithmic output entropy.  That is, fuzzy min-entropy is both a necessary and \emph{sufficient} condition for security in this setting.

\textbf{Distribution-Oblivious} The distribution-oblivious situation is more complicated.  Indeed, there is a significant difference between secure sketches and fuzzy extractors.  We show that there exist families of distributions where each distribution has fuzzy min-entropy such that any secure sketch is insecure.  However, it is possible to build a fuzzy extractor for these same family of distributions.
\end{abstract}

@@

The paradigm for performing noisy key derivation using a single metric is known as fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08}.  Consider a particular high entropy distribution $W$.  Our goal is to derive stable keys from $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.  A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes the initial reading $w$ and produces $key$ along with a public helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.  The $key$ must be strong even to an adversary that has observed $p$~(the problem is trivial if $p$ is private).

Traditionally, fuzzy extractors are constructed by using a separate information-reconciliation component, known as a secure sketch, that maps $w'$ back to $w$ and a privacy-amplification component, a strong randomness extractor~\cite{nisan1993randomness}, that maps $w$ to a random key.  These objects can either be information-theoretic or computational.  The computational versions of these objects are defined in~\cite{krawczyk2010cryptographic} and~\cite{fuller2013computational} respectively.  Fuller et al.~\cite{fuller2013computational} show that computational secure sketches are unlikely to improve significantly on information-theoretic secure sketches.

\textbf{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.  If the error-tolerance allows the entire metric space to authenticate then no security is possible.  As an example, consider a distribution $W$, where the adversary attempts to learn the key simply by inputting a point to the reproduce function.  Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.  For a fuzzy extractor to be secure this must occur with negligible probability.  That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.  Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.  We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.  The fuzzy min-entropy of a distribution must be super-logarithmic for any reasonable of either a fuzzy extractor~(\lemref{lem:fuzz necessary}).

In the more general interactive setting where two parties hold $w$ and $w'$ and wish to agree on a common key, fuzzy min-entropy is both a necessary and sufficient condition~(using two-party computation). 
However, in the one-message setting we are far from achieving security whenever fuzzy min-entropy is high.

Traditional fuzzy extractors and secure sketches incur at entropy loss of the size of the ball to be error-corrected.  While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.  As an example, many examples that arise in practice there are more error patterns than starting entropy.  Traditional fuzzy extractors provide no guarantee for sources of this type.  The work of Canetti et al.~\cite{canetti2014key} shows it is possible to provide build fuzzy extractors for some distributions with this property.  Their work leaves the question open for a large number of distributions.  This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}

When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.  However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).  This uncertainty is usually expressed by proving the fuzzy extractor works for a class of distributions with some known property~(such as entropy and error levels).  In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.  We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}

\textbf{Our Contribution} We show that for every distribution with super-logarithmic fuzzy min-entropy it is information-theoretically possible to build a secure sketch that retains super-logarithmic min-entropy.  Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.  (A key with super-logarithmic entropy can be expanded to arbitrary length using computational techniques.)  For distribution-aware secure sketches and fuzzy extractors, fuzzy min-entropy is both a necessary and sufficient condition for security.

The situation is significantly more complicated for distribution-oblivious algorithms.  Indeed, we show that there natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.  However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.

\textbf{Note:} Our constructions are information-theoretic and do not run in polynomial time.  They should primarily be regarded as feasibility results.  Our negative results apply to algorithms even given arbitrary running time, thus there is clear separation for unbounded running time algorithms.  It remains as an open question whether our distribution-aware results can be replicated by efficient algorithms.  This seems unlikely as most  interesting distributions have exponential size description.  The power of the distribution-aware setting is that the algorithms can access this description.  It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.

\textbf{Open Problems:} We showed that in the distribution-oblivious setting there is a separation between a secure sketch and a fuzzy extractor.  However, it is still not known if fuzzy extractors can be constructed for any family of distributions.

\begin{table}
\begin{center}
\begin{tabular}{c | c | c }
& Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No\\
\hline
Fuzzy Extractor & Yes~(\thref{cons:leveling}) & Yes for some families\\
& & Unknown for arbitrary family
%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient for extraction?}
\label{tab:main results}
\end{table}

\bnote{connection to obfuscation}
\section{Preliminaries}
\label{sec:preliminaries}
\bnote{be careful with overloading of $\ell$, both key length and number of levels.}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\ell$  the tuple $(X_1,\dots, X_\ell)$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We will also use an average case version of this notion~(to the best of our understanding this has not been used before):\bnote{has it?}
\begin{definition}[Conditional Hartley Entropy]
\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$.

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\ell$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.  For this metric, $|B_t| = \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

\section{Fuzzy Extractors}\label{sec:fuzz extractor}

We now recall definitions and lemmas from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08}, adapted to allow for a small probability of error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08}.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, m, \ell, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\ell$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that for $w$ and $w'$ such that $\dis(w,w')\leq t$, if $R,P$ were generated by $(R,P)\leftarrow\gen(w)$, then $\rep(w',P)=R$ with probability~(over the coins of $\gen, \rep$) at least $1-\delta$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rep.
\item The \emph{security} property guarantees that for any distribution $W$ on $\mathcal{M}$ of min-entropy $m$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\ell,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distance results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.  A fuzzy extractor performs two tasks, producing a uniform key and providing error-tolerance.  Traditional, the uniform key is produced by extraction from the original secret $w$ and the error-tolerance is obtained by using a secure sketch.  Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},m, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that if $\dis(w,w')\leq t$, then $\Pr[\rec(w',\sketch(w))=w]\geq 1-\delta$ where the probability is taken over the coins of $\sketch$ and $\rec$.  If $\dis(w,w')>t$, then no guarantee is provided about the output of \rec.
\item The \emph{security} property guarantees that for any distribution $W$ over $\mathcal{M}$ with min-entropy $m$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

\textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.  We do not consider a computational version of secure sketches. Fuller et al. showed that computational secure sketches imply information-theoretic secure sketches with almost the same parameters~\cite[Corollary 3.8]{fuller2013computational}.

A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}. An average-case extractor is a generalization of a strong randomness extractor \cite[Definition 2]{nisan1993randomness}) (in particular, Vadhan~\cite[Problem 6.8]{Vad12} showed that all strong extractors are average-case extractors with a slight loss of parameters):
\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\ell$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\ell\times
U_d \times Y) \le \epsilon$.
\end{definition}

\begin{lemma}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, m, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\ell$ be a $(\tilde{m}, \epsilon)$-average-case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, m, \ell, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}

\subsection{A necessary condition for security}
\label{sec:minimal conditions}
Consider the functionality of a fuzzy extractor, the reproduce algorithm produces the same key when provided with a nearby input point.  In an ideal world, this would be all that is revealed by the reproduce algorithm.  For the remainder of this work, we compare security with this ideal world.  This ideal world can be expressed by an adversary providing a ``guess'' point to the algorithm~(and hoping that their guess was closed to the stored point).  We call the level of security in this setting, fuzzy min-entropy.
%\todo{doesn't 2PC require assumptions?}
%We now define fuzzy min-entropy and show that fuzzy extractor security is only possible when the fuzzy min-entropy is super-logarithmic.

>>>>

 \documentclass[11pt]{article}

\def\shownotes{1}
\def\blinded{0}

@@

\ifnum\shownotes=1
\newcommand{\authnote}[2]{{\textcolor{red}{\textsf{#1 notes: }\textcolor{blue}{ #2}}\marginpar{\textcolor{red}{\textbf{!!!!!}}}}}
\else
\newcommand{\authnote}[2]{}
\fi

\ifnum\blinded=0
\newcommand{\blind}[1]{{#1}}
\else
\newcommand{\blind}[1]{}
\def\shownotes{0}
\fi

\newcommand{\bnote}[1]{{\authnote{Ben}{#1}}}
\newcommand{\lnote}[1]{{\authnote{Leo}{#1}}}
\newcommand{\anote}[1]{{\authnote{Adam}{#1}}}

@@

\title{When are Fuzzy Extractors Possible?}
\blind{
\author{Benjamin Fuller\footnote{Boston University and MIT Lincoln Laboratory. The Lincoln Laboratory portion of this
work was sponsored by the Department of the Air Force under Air Force
Contract
\#FA8721-05-C-0002.  Opinions,
interpretations, conclusions and recommendations are those of the author
and
are not necessarily endorsed by the United States Government.  Email: {\tt bfuller@cs.bu.edu}.}~~~~~~~~~~Leonid Reyzin\footnote{Boston University.  Email: {\tt reyzin@cs.bu.edu}.}~~~~~~~~~~Adam Smith\footnote{Pennsylvania State University. Work done in part while the author was at Boston University and Harvard University.  Email: {\tt asmith@psu.edu}.  }}
}
\begin{document}
\maketitle

@@

Ideally, key derivation should be possible whenever a negligible portion of $W$ lies within a ball~(arbitrarily centered) of radius $t$.  We call the maximum weight that lies within any ball of radius $t$ the fuzzy min-entropy of a distribution.  In the interactive setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

Current techniques for constructing fuzzy extractors lie far from this necessary condition.  We investigate whether this is inherent for both fuzzy extractors and secure sketches~(a one round information-reconciliation component).  Our constructions and impossibility results are information-theoretic.

We consider two types of fuzzy extractors and secure sketches.  The first we call \emph{distribution-aware}, the algorithms know the precise distribution they are trying to correct.  The second is \emph{distribution-oblivious} where $(\gen, \rep)$ must work for a family of distributions.

\textbf{Distribution-Aware} Whenever the fuzzy min-entropy is super-logarithmic, there exists a distribution-aware secure sketch and fuzzy extractor with super-logarithmic output entropy.  That is, fuzzy min-entropy is both a necessary and \emph{sufficient} condition for security in this setting.

\textbf{Distribution-Oblivious} The distribution-oblivious situation is more complicated.  Indeed, there is a significant difference between secure sketches and fuzzy extractors.  We show that there exist families of distributions where each distribution has fuzzy min-entropy such that any secure sketch is insecure.  However, it is possible to build a fuzzy extractor for these same family of distributions.
\bnote{come back to this.}
\end{abstract}

@@

The paradigm for performing noisy key derivation using a single message is known as fuzzy extractors~\cite{DBLP:journals/siamcomp/DodisORS08}.  Consider a particular high entropy distribution $W$.  Our goal is to derive stable keys from $W$ whenever the two readings~(denoted $w$ and $w'$ respectively) are within distance $t$.  A fuzzy extractor consists of two algorithms: generate~($\gen$) which takes the initial reading $w$ and produces $key$ along with a public helper value $p$.  The reproduce~($\rep$) algorithm takes the subsequent reading $w'$ along with the helper value $p$ to reproduce $key$.  The $key$ must be strong even to an adversary that has observed $p$~(the problem is trivial if $p$ is private).

Traditionally, fuzzy extractors are constructed by using a separate information-reconciliation component, known as a secure sketch, that maps $w'$ back to $w$ and a privacy-amplification component, a strong randomness extractor~\cite{nisan1993randomness}, that maps $w$ to a random key.  These objects can either be information-theoretic or computational.  The computational versions of these objects are defined in~\cite{fuller2013computational} and~\cite{krawczyk2010cryptographic} respectively.  Fuller et al.~\cite{fuller2013computational} show that computational secure sketches are unlikely to improve significantly on information-theoretic secure sketches.

\textbf{A Necessary Condition:}  Intuitively, error-tolerance and key strength are at odds.  Fix some distribution $W$.  The adversary has access to the reproduce function and attempts to learn the key by inputting a point.  Let $x^*$ be the point input by the adversary, the adversary learns the correct key whenever $\dis(w, x^*)\le t$.  For security, this must occur with negligible probability.  That is, a negligible portion of the probability mass of $W$ may be close to any point in the metric space.  Mathematically, for all $x^*, \sum_{w\in W | \dis(w, x^*)\le t} \Pr[ W= w] \le \ngl(n)$.  We call the negative logarithm of this quantity the \emph{fuzzy min-entropy} of a distribution.  A distribution must have super-logarithmic fuzzy min-entropy for a fuzzy extractor or a secure sketch  to provide meaningful security~(\lemref{lem:fuzz necessary}).

In the interactive setting where two parties hold $w$ and $w'$ and wish to agree on a common key, fuzzy min-entropy is both a necessary and sufficient condition~(using secure two-party computation). 
However, in the one-message setting we are far from achieving security whenever fuzzy min-entropy is high.

Traditional fuzzy extractors and secure sketches operate in the worst case and incur entropy loss of the size of the ball to be error-corrected.  While, this is optimal for the uniform distribution, it is far from optimal for distributions that arise in practice.  As an example, many examples that arise in practice there are more error patterns than starting entropy.  Traditional fuzzy extractors provide no guarantee for sources of this type.  The work of Canetti et al.~\cite{canetti2014key} constructs fuzzy  extractors for some distributions with more errors than entropy.  This leads to the following natural question: \emph{when is key derivation from noisy sources possible?}

\paragraph{Codifying distributional uncertainty}
When building a fuzzy extractor, the algorithm designer has some information about the distribution $W$ that will be used.  However, rarely does the algorithm designer know the entire description of $W$'s probability distribution~(indeed this description may be exponential size).  Thus, fuzzy extractors are designed to work for a class of distributions with some known property~(such as entropy and error levels).  As long as the distribution falls in this class, security and correctness hold.

To characterize key derivation from noisy sources, we consider the effect of this uncertainty.  We consider two settings, the first is the standard setting where the algorithms must work for a class of distributions.  We call this setting \emph{distribution-oblivious}.  In the second, we allow the algorithms complete knowledge of the distribution.  We call this setting \emph{distribution-aware}.

%In this work, we discriminate between fuzzy extractors and secure sketches that are allowed to know the distribution of $W$ and algorithms that are required to work for a family of distributions $\mathcal{W}$.  We call the first type of algorithm \emph{distribution-aware} and the second type \emph{distribution-oblivious}

\textbf{Our Contribution} In the \emph{distribution-aware} setting, for every source with super-logarithmic fuzzy min-entropy it is possible to build a secure sketch with super-logarithmic output entropy~(\thref{cons:leveling}).  Using standard techniques we can convert this secure sketch to a fuzzy extractor with super-logarithmic key output length.  (A key with super-logarithmic entropy can be expanded to arbitrary length using computational techniques.)  Thus, in the distribution-aware setting, fuzzy min-entropy is both a necessary and sufficient condition for security.

\textbf{Note:} Our constructions are information-theoretic and do not run in polynomial time.  They should be regarded as feasibility results.  It is unclear how to define distribution-aware efficient algorithms as most distributions have exponential description size.  The power of the distribution-aware setting is that the algorithms can access this description.  It seems unlikely that algorithms with access to a polynomial size part of the distribution description can replicate these results.

We show that distributional uncertainty is a real drawback to providing security.  In the standard \emph{distribution-aware} setting, we show a family of distributions~(each with super-logarithmic fuzzy min-entropy) such that any secure sketch for the family is insecure~(\thref{thm:imposs sketch}).  This negative result extends to computational secure sketches~\bnote{cite a corollary}.

%The situation is significantly more complicated for distribution-oblivious algorithms.  Indeed, we show a natural families to distributions where every distribution has fuzzy min-entropy such that no secure sketch can provide meaningful security.  However, it is possible to build a meaningful fuzzy extractor for this same class of distributions.

\textbf{Open Problem:} The main open problem is whether fuzzy min-entropy is a sufficient condition for constructing a fuzzy extractor in the distribution-oblivious setting.  We note that it is known how to build a fuzzy extractor for the family of distributions used in our negative result~\cite[Theorem 5.7]{canetti2014key}.  Furthermore, are computational assumptions necessary?
\bnote{talk about obfuscation.}

\begin{table}
\begin{center}
\begin{tabular}{c | c | c }
& Distribution-Aware & Distribution-Oblivious\\
\hline
Secure Sketch & Yes~(\thref{cons:leveling}) & No~(\thref{thm:imposs sketch})\\
\hline
Fuzzy Extractor & Yes~(\corref{cor:extension to fuzz ext}) & Unknown
%Flat distribution & $\Hfuzz(W) - \log (1/\delta)$ &$\log |B_t|$\\
%Arbitrary distribution & $\Hfuzz(W) - \log (1/\delta) - \log \log \mathcal{M}$ & $\log |B_t|$
\end{tabular}
\end{center}
\caption{Is fuzzy min-entropy sufficient for extraction?}
\label{tab:main results}
\end{table}

\paragraph{Organization} The reminder of the paper is organized as follows.  In \secref{sec:preliminaries}, we cover preliminaries and fuzzy extractor definitions.  In \secref{sec:distribution aware}, we described the distribution aware setting, and show a construction for an arbitrary distribution with fuzzy min-entropy.  Finally, in \secref{sec:dist oblivious} we provide negative results for the distribution-oblivious setting.

\section{Preliminaries}
\label{sec:preliminaries}
For a random variables $X_i$ over some alphabet $\mathcal{Z}$ we denote by $X = X_1,..., X_\gamma$  the tuple $(X_1,\dots, X_\gamma)$.  For a set of indices $J$, $X_{J}$ is the restriction of $X$ to the indices in $J$.  The set $J^c$ is the complement of $J$.  Unless otherwise noted logarithms are base $2$.
Usually, we use capitalized letters for random variables and corresponding lowercase letters for their samples.

The {\em min-entropy} of $X$ is $\Hoo(X) = -\log(\max_x \Pr[X=x])$,
and the {\em average (conditional)} min-entropy of $X$ given $Y$ is  $\Hav(X|Y) = -\log(\expe_{y\in Y} \max_{x} \Pr[X=x|Y=y])$~\cite[Section 2.4]{DBLP:journals/siamcomp/DodisORS08}.   For a random variable $W$, let $H_0(W)$ be the logarithm of the size of the support of $W$,  that is $H_0(W) = \log |\{w | \Pr[W=w]>0\}|$.  We will also use an average case version of this notion~(to the best of our understanding this has not defined used before):\bnote{has it?}
\begin{definition}[Conditional Hartley Entropy]
\label{def:conditional hartley}
The conditional Hartley entropy of $X |Y $ is $\tilde{H}_0(X |Y) = \log ( \expe_{y\in Y} |\{x | \Pr[X=x |Y=y]>0\}|)$.
\end{definition}
The {\em statistical distance} between random variables $X$ and $Y$ with the same domain is $\Delta(X,Y) = \frac12 \sum_x |\Pr[X=x] - \Pr[Y=x]|$.
For a distinguisher $D$ we write the \emph{computational distance} between $X$ and $Y$ as $\delta^D(X,Y) = \left| \expe[D(X)]-\expe[D(Y)]\right |$ (we extend it to a class of distinguishers $\mathcal{D}$ by taking the maximum over all distinguishers $D\in\mathcal{D}$).  We denote by $\mathcal{D}_{s}$ the class of randomized circuits which output a single bit and have size at most $s$. \bnote{there is nothing computational here right now}

For a metric space $(\mathcal{M}, \dis)$, the \emph{(closed) ball of radius $t$ around $x$} is the set of all points within radius $t$, that is, $B_t(x) = \{y| \dis(x, y)\leq t\}$.  If the size of a ball in a metric space does not depend on $x$, we denote by $|B_t|$ the size of a ball of radius $t$.  We consider the Hamming metric over vectors in $\mathcal{Z}^\gamma$, defined via $\dis(x,y) = \{i | x_i \neq y_i\}$.  For this metric, $|B_t| = \sum_{i=0}^t {\gamma \choose i} (|\mathcal{Z}|-1)^i $.  $U_n$ denotes the uniformly  distributed random variable on $\{0,1\}^n$.  For the remainder of this work we consider a sequence of metric spaces $\mathcal{M}_n$ parameterized by $n$, but we write $\mathcal{M}$ for notational convenience.

\subsection{Fuzzy Extractors}\label{sec:fuzz extractor}

We recall definitions and lemmas from the work of Dodis et. al.~\cite[Sections 2.5--4.1]{DBLP:journals/siamcomp/DodisORS08} with two changes.  First we allow for error, as discussed in \cite[Sections 8]{DBLP:journals/siamcomp/DodisORS08} and we consider an arbitrary family $\mathcal{W}$ of distributions instead of families containing all distributions of a given min-entropy.  See~\cite{canetti2014key} for discussion.  Let $\mathcal{M}$ be a metric space with distance function $\dis$.

\begin{definition}
\label{def:fuzzy extractor}
An $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-\emph{fuzzy extractor} with error $\delta$ is a pair of randomized procedures, ``generate'' $(\gen)$ and ``reproduce'' $(\rep)$, with the following properties: 
\begin{enumerate}
\item The generate procedure \gen on input $w\in \mathcal{M}$ outputs an extracted string $r\in\{0,1\}^\kappa$ and a helper string $p\in\{0,1\}^*$.
\item The reproduction procedure \rep takes an element $w'\in \mathcal{M}$ and a bit string $p\in\{0,1\}^*$ as inputs.  The \emph{correctness} property of fuzzy extractors guarantees that
\[
\forall w, w'\in \mathcal{M}, \dis(w, w')\le t \Rightarrow \Pr[(R, P)\leftarrow \gen(w) \wedge \rep(w', P) =R] \ge 1-\delta
\]
where the probability is taken over the coins of $\gen, \rep$.
\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the string $R$ is nearly uniform even for those who observe $P$:  if $(R,P)\leftarrow\gen (W)$, then $\mathbf{SD}((R,P),(U_\kappa,P))\leq \epsilon$.
\end{enumerate}
A fuzzy extractor is efficient if $\gen$ and $\rep$ run in expected polynomial time.
\end{definition}

Replacing the statistical distance in \defref{def:fuzzy extractor} with computational distance results in a \emph{computational fuzzy extractor}~\cite[Definition 2.5]{fuller2013computational}.  A fuzzy extractor performs two tasks, producing a uniform key and providing error-tolerance.  Traditional, the uniform key is produced by extraction from the original secret $w$ and the error-tolerance is obtained by using a secure sketch.  Secure sketches produce a string $s$ that does not decrease the entropy of $w$ too much, while allowing recovery of $w$ from a  close $w'$:
\begin{definition}
\label{def:secure sketch}
An $(\mathcal{M},\mathcal{W}, \tilde{m}, t)$-\emph{secure sketch} with error $\delta$ is a pair of randomized procedures, ``sketch'' $(\sketch)$ and ``recover'' $(\rec)$, with the following properties:
\begin{enumerate}
\item The sketching procedure \sketch on input $w\in\mathcal{M}$ returns a bit string $s\in\{0,1\}^*$.
\item The recovery procedure \rec takes an element $w'\in\mathcal{M}$ and a bit string $s\in\{0,1\}^*$.  The \emph{correctness} property of secure sketches guarantees that 
\[
 \forall w, w'\in\mathcal{M}, \dis(w,w')\leq t \Rightarrow \Pr[\rec(w',\sketch(w))=w]\geq 1-\delta
 \] 
where the probability is taken over the coins of $\sketch$ and $\rec$.  
\item The \emph{security} property guarantees that for any distribution $W\in\mathcal{W}$, the value of $W$ can be recovered by the adversary who observes $w$ with probability no greater than $2^{-\tilde{m}}$.  That is, $\Hav(W|\sketch(W))\geq \tilde{m}$.
\end{enumerate}
A secure sketch is \emph{efficient} if \sketch and \rec run in expected polynomial time. 
\end{definition}

\textbf{Notes:} In the above definition of secure sketches (resp., fuzzy extractors), the errors are chosen before $s$ (resp., $P$) is known: if the error pattern between $w$ and $w'$ depends on the output of $\sketch$ (resp., $\gen$), then there is no guarantee about the probability of correctness.

A fuzzy extractor can be produced from a \emph{secure sketch} and an \emph{average-case randomness extractor}:

\begin{definition}
Let $\chi_1$, $\chi_2$ be finite sets.
A function $\ext: \chi_1\times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon)$-average-case extractor} if for all pairs
of random variables $X, Y$ over $\chi_1, \chi_2$ such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\Delta((\ext(X, U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

\begin{lemma}
\label{lem:fuzzy ext construction}
Assume $(\sketch, \rec)$ is an $(\mathcal{M}, \mathcal{W}, \tilde{m}, t)$-secure sketch with error $\delta$, and let $\ext:\mathcal{M}\times \zo^d \rightarrow \zo^\kappa$ be a $(\tilde{m}, \epsilon)$-average-case extractor.  Then the following $(\gen, \rep)$ is an $(\mathcal{M}, \mathcal{W}, \kappa, t, \epsilon)$-fuzzy extractor with error $\delta$:
\begin{itemize}
\item $\gen(w):$ generate $x\leftarrow \zo^d$, set $p=(\sketch(w), x), r=\ext(w;x)$, and output $(r,p)$.
\item $\rep(w', (s, x)):$ recover $w=\rec(w',s)$ and output $r=\ext(w;x)$.
\end{itemize}
\end{lemma}

\subsection{A necessary condition for security}
\label{sec:minimal conditions}
